---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
load("D:/MS/STA 541 (Multivariate Statistical Methods)/PCcars.Rdata")
x=PCcars
x
fit=prcomp(x, scale=TRUE)
fit
```

```{r}
fit$rotation
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. Something to be deleted.

```{r}
(fit$sdev)^2   #Variance of the components 
```

```{r}
summary(fit)
```

```{r}
screeplot(fit, type= "lines")
```



I would keep the first 3 components for this analysis. From the summary, we see that almost 91% of variation is explained by the first 3 components. We can also see the evidence from the screeplot diagram. 

PC1 - Different features of cars (cyl, disp, hp)
PC2 - Fuel consumption of cars (Miles per (US) gallon)


```{r}
library(ggplot2)
library(factoextra)
fviz_pca_var(fit)
```

```{r}
fviz_mfa_ind(fit)
```

```{r}
fviz_pca(fit)
```

Types of Car at the bottom have more more fuel consumption rate.
Types of Car at right have have high number of cylinders ('cyl'), high Displacement ('disp') and high number of Gross horsepower ('hp').
Types of Car close to zero on both components have approximately average levels of both features of cars and fuel consumption. 








